---
format: 
  pdf: 
    number-sections: true
execute: 
  echo: false
  message: false
  warning: false
---

```{r}
library(tidyverse)
library(kableExtra)
```

# Results {#sec:results}

```{r}
experiment <- read_csv("data/data.csv")
```

```{r}
# Convert veggie_label into factor
experiment <- experiment %>%
  mutate(veggie_label = factor(
    veggie_label,
    levels = c("standard",
               "organic",
               "sustainable",
               "organic-sustainable")
    ))
```

## Descriptive results

### Sample

```{r subjects}
subjects <- experiment %>% 
  distinct(subject, italian)
```

During the duration of the experiment, a total of `r nrow(subjects)` students consumed at least one meal at the canteen.
The majority of students had Italian nationality (`r round(mean(subjects$italian)*100)` percent).

### Canteen attendance

```{r}
median_attendance <- experiment %>%
  group_by(subject) %>%
  summarize(N = n()) %>% 
  pull(N) %>% 
  median()

max_attendance <- experiment %>%
  group_by(subject) %>%
  summarize(N = n()) %>% 
  pull(N) %>% 
  max()
```

```{r}
#| label: fig-histogram
#| fig-align: center
#| out-width: 90%, fig.align='center'
#| fig-cap: "Histogram of the number of days a student attended the canteen for a lunch meal."

experiment %>%
  group_by(subject) %>%
  mutate(N = n()) %>%
  distinct(subject, N) %>%
  ggplot() +
  aes(x = N) +
  geom_histogram(binwidth = 1,
                 color = "white",
                 fill = "#8174a1") +
  theme_bw() +
  labs(x = "Number of days a student attended the canteen",
       y = "Count") +
  scale_x_continuous(limits = c(0, 31),
                     breaks = seq(1, 31, by = 2))
```

@fig-histogram is a histogram of the number of days during the main study that a student attended the canteen for a lunch meal.
Fifty percent of students attended the canteen as most `r median_attendance` times, corresponding to (`r round(median_attendance/31 * 100)`) percent of 31 possible days to attend during the main study.
One student ate at the canteen on `r max_attendance` days, which was the maximum number of canteen visits during the main study.

```{r}
#| label: tbl-crude-prop
#| tbl-cap: "Percentage of ordering at least one vegatable plate per menu day by plate labels."

veg_orders_summary <- experiment %>% 
  group_by(veggie_label) %>% 
  summarize(
    proportion_veg = mean(response)*100,
    n_orders = length(response)
  )

knitr::kable(
  veg_orders_summary,
  format = "latex",
  escape = FALSE,
  booktabs = TRUE,
  col.names = c(
    "Label",
    "Vegetable plate (\\%)",
    "Total orders"
  ),
  align =  c("c", "c"),
  digits = 2
) %>%
  kable_styling(latex_options = "HOLD_position")

```

@tbl-crude-prop summarizes the crude proportions of ordering at least one vegetable item per menu day by vegetable label type, across all menu days of the study.

