---
format: 
  pdf: 
    number-sections: true
execute: 
  echo: false
  message: false
  warning: false
---

```{r}

# LOAD LIBRARIES HERE

```

# Results {#sec:results}

```{r}

# LOAD DATA HERE

```


## Descriptive results

### Sample

During the duration of the experiment, a total of **XXXX** students consumed at least one meal at the canteen.
The majority of students had Italian nationality (**XXXX** percent).

### Canteen attendance

```{r}

# MEDIAN AND MODE OF CANTEEN ATTENDANCE

```

```{r}

# MAKE HISTOGRAM HERE

```

@fig-histogram is a histogram of the number of days during the main study that a student attended the canteen for a lunch meal.
Fifty percent of students attended the canteen as most **XXXXX** times, corresponding to (**r round(median_attendance/31 * 100)**) percent of 31 possible days to attend during the main study.
One student ate at the canteen on **r max_attendance days**, which was the maximum number of canteen visits during the main study.

```{r}

# MAKE TABLE HERE

```

**TABLE XXXXX** summarizes the crude proportions of ordering at least one vegetable item per menu day by vegetable label type, across all menu days of the study.

